Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2022-09-20 ba_resubmit/kundinger_resubmit.tex
update.

\textcolor{blue}{In practice, it is not feasible to make all-to-all record comparisons as the computational complexity is of order $O(n_1 \times n_2).$ The most common solution is to utilize blocking, which places similar records into partitions, or ``blocks,'' to reduce this computational burden \citep{steorts_comparison_2014, murray2016probabilistic}. In deterministic blocking, the modeler chooses a field thought to be highly reliable, and only compares records that agree on that field. The record linkage method is then applied independently across all blocks, which can be done in parallel for additional speed gains. However, blocking on an unreliable field can lead to missed matches, making this form of blocking undesirable in some situations \citep{steorts_comparison_2014}.}

@@

\textcolor{red}{(I don't love this right here, but I don't really know where else to put it. But if it won't cause a problem with the reviewers, I'll just leave it.)}
\textcolor{blue}{Perhaps any parts that aren't needed can be removed. I'll take a stab at it.}

>>>>

\textcolor{blue}{In practice, it is not feasible to make all-to-all record comparisons as the computational complexity is of order $O(n_1 \times n_2),$ where $n_1$ and $n_2$ are the sizes of each database. The most common solution is to utilize blocking, which places similar records into partitions, or ``blocks,'' to reduce this computational burden \citep{steorts_comparison_2014, murray2016probabilistic}. In deterministic blocking, the modeler chooses a field thought to be highly reliable, and only compares records that agree on that field. The record linkage method is then applied independently across all blocks, which can be done in parallel for additional speed gains. However, blocking on an unreliable field can lead to missed matches, making this form of blocking undesirable in some situations \citep{steorts_comparison_2014}.}

@@

%\textcolor{red}{(I don't love this right here, but I don't really know where else to put it. But if it won't cause a problem with the reviewers, I'll just leave it.)}
%\textcolor{blue}{Perhaps any parts that aren't needed can be removed. I'll take a stab at it.}
